---
title: "Capstone Presentation: Yelp Data Set"
author: "Jacob Townson"
date: "02/20/2015"
output: ioslides_presentation
---

```{r include=FALSE}
require(mosaic)
```

## Question

Is there a correlation between the frequency of how often someone reviews on Yelp and the amount they travel? If so, do more frequent reviewers travel more than non-frequent reviewers based off of the cities and coordinates they review at?

Why is this interesting? 

- It could be helpful for organizational purposes on Yelp. If more frequent users travel more, maybe they could make recommendations of organizations for users to visit when they travel. 

## Methods

- The methodology of this project began with a massive amount of cleaning data. The end product was a dataframe that consisted only of the user ids, the number of cities visited, the maximum radius of travel, and the number of reviews made. 

- The models were made using the lm function in R:

```{r}

```


## Results



## Discussion













